\bf Visual Inference for a Social Network Model

### 2019-01-25 ASApaper/paper.Rnw
some rearranging, re-write abstract.

\documentclass[12pt]{article}
% \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
% \geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\usepackage{graphicx}
\usepackage[font=small,skip=5pt]{caption}
\usepackage{subcaption}
\usepackage{animate}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
% \usepackage{color}
\usepackage{multirow}
\usepackage{rotating}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{hyperref}
\graphicspath{{figure/}}
% \usepackage{endfloat} % Figures to the end of the document

@@

\if0\blind
{
  \title{\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model}
  \author{Samantha Tyner\thanks{
    The authors gratefully acknowledge funding from the National Science Foundation Grant \# DMS 1007697. All data collection has been conducted with approval from the Institutional Review Board IRB 10-347}\hspace{.2cm}\\
    Department of Statistics and Statistical Laboratory, Iowa State University\\
    and \\
    Heike Hofmann\\
    Department of Statistics and Statistical Laboratory, Iowa State University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
Abstract goes here.
\end{abstract}

@@

\tableofcontents
\newpage

<<child-demo, child='paper-child.Rnw'>>=
@

>>>>

\documentclass[12pt]{article}
% \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
% \geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\usepackage{graphicx}
\usepackage[font=small,skip=5pt]{caption}
\usepackage{subcaption}
%\usepackage{animate}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
%\usepackage{color}
\usepackage{multirow}
\usepackage{rotating}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{hyperref}
\usepackage{numprint}

\graphicspath{{figure/}}
% \usepackage{endfloat} % Figures to the end of the document
\newcommand{\st}[1]{{\color{orange} #1}}
\newcommand{\hh}[1]{{\color{magenta} #1}}

@@

\if0\blind
{
  \title{\bf Visual Inference for a Social Network Model}
  \author{Samantha Tyner\thanks{
    The authors gratefully acknowledge funding from the National Science Foundation Grant \# DMS 1007697. All data collection has been conducted with approval from the Institutional Review Board IRB 10-347}\hspace{.2cm}\\
    Department of Statistics and Statistical Laboratory, Iowa State University\\
    and \\
    Heike Hofmann\\
    Department of Statistics and Statistical Laboratory, Iowa State University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visual Inference for a Social Network Model}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
Three of the most important assessments of a statistical model are significance tests of parameters, goodness-of-fit tests, and power calculations of the tests. All three tasks become more difficult as the model becomes more complex. We will explore the three assessments of one particularly complex set of models, continuous time Markov chain (CTMC) models, for dynamic social networks  \citep{saompaper}. In this paper, we propose new methods for significance and goodness-of-fit testing, as well as power calculation for CTMC models via the visual inference (VI) paradigm of \citet{Bujaetal}. With VI, we can look at entire datasets simulated from a model, instead of relying a single metric such as a $p$-value for a single parameter in the model or goodness-of-fit assessed by looking at outdegree. We conducted an experiment through Amazon Mechanical Turk to assess the significance of parameters, the fit of a model, and the visual power of parameters.  
\end{abstract}

@@

%\tableofcontents
\newpage

<<child-demo, child='paper-child-thesis-ch-2.Rnw'>>=
@
